---
title: "Belief Agreement and Stability"
output:
  html_document:
    df_print: paged
---

```{r, include = F}
library(easypackages)
libraries("tidyverse", "ggplot2", "scales", "knitr", "kableExtra", "lme4", "lmerTest", "rmcorr")

rm(list = ls())

df <- readRDS(file = "S:\\TRACK to TREAT\\Data\\Processed Data\\depression_belief_data.rds") %>%
  select(-matches("def_"),
         -matches("other_text$"),
         -pb_childethnicity_alt)

# Standardize depression belief variables
df <- df %>%
  mutate(across(yb_depPermanence:p3m_lessPermOther, 
                ~ . %>% 
                  scale() %>%
                  as.numeric()))

# Create numeric version of income
df <- df %>%
  mutate(pb_income_num = case_when(
    pb_income == "$0-$19,000" ~ 1,
    pb_income == "$20,000-$39,000" ~ 2,
    pb_income == "$40,000-$59,000" ~ 3,
    pb_income == "$60,000-$79,000" ~ 4,
    pb_income == "$80,000 - $99,000" ~ 5,
    pb_income == "$100,000 - $119,000" ~ 6,
    pb_income == "$120,000-$140,000" ~ 7,
    pb_income == "$140,000+" ~ 8
  ))
```

## Sample Description

```{r, echo = F}
count(df, pb_childethnicity) %>%
  mutate(prop = n / sum(n))
count(df, pb_childgender) %>%
  mutate(prop = n / sum(n))
count(df, pb_childage) %>%
  mutate(prop = n / sum(n))
count(df, pb_income) %>%
  mutate(prop = n / sum(n))
```

## Analysis 1: Child Beliefs and Child Demographics

Repeated measures (hierarchical) linear regression (lmer)

```{r}
# Belief outcomes - we will run regressions for each of these
beliefs <- c("depPermanence", "causeBrain", "causeEnv", "changeBrain", "changeEnv", "lessPermTherapy", "lessPermMed")

# Ethnicity levels with N >= 10
ethnicity_levels <- c("White, non-Hispanic (includes Middle Eastern)",
                      "Black or African American",
                      "Hispanic or Latino/a",
                      "More than one race")

# Gender levels with N >= 10
gender_levels <- c("girl/woman", "boy/man")

out_1 <- tibble()

for(y in beliefs) {

  # Ethnicity
  model <- df %>%
    filter(pb_childethnicity %in% ethnicity_levels) %>%
    mutate(pb_childethnicity = factor(pb_childethnicity, ethnicity_levels)) %>%
    pivot_longer(matches(paste0("y.*", y))) %>%
    lmerTest::lmer(data = .,
                   formula = value ~ pb_childethnicity + (1 | yb_lsmh_id)) %>%
    summary()
  
  coefficients <- model$coefficients[-1,]
  
  results <- tibble(
    DV = y,
    IV = rownames(coefficients),
    est = coefficients[,"Estimate"],
    se = coefficients[,"Std. Error"],
    p = coefficients[,"Pr(>|t|)"]
  )
  
  out_1 <- rbind(out_1, results)
  
  # Gender
  model <- df %>%
    filter(pb_childgender %in% gender_levels) %>%
    mutate(pb_childgender = factor(pb_childgender, gender_levels)) %>%
    pivot_longer(matches(paste0("y.*", y))) %>%
    lmerTest::lmer(data = .,
                   formula = value ~ pb_childgender + (1 | yb_lsmh_id)) %>%
    summary()
  
  coefficients <- model$coefficients[-1,]
  
  results <- tibble(
    DV = y,
    IV = "pb_childgenderboy/man",
    est = coefficients["Estimate"],
    se = coefficients["Std. Error"],
    p = coefficients["Pr(>|t|)"]
  )
  
  out_1 <- rbind(out_1, results)
  
  # Age
  model <- df %>%
    drop_na(pb_childage) %>%
    pivot_longer(matches(paste0("y.*", y))) %>%
    lmerTest::lmer(data = .,
                   formula = value ~ pb_childage + (1 | yb_lsmh_id)) %>%
    summary()
  
  coefficients <- model$coefficients[-1,]
  
  results <- tibble(
    DV = y,
    IV = "pb_childage",
    est = coefficients["Estimate"],
    se = coefficients["Std. Error"],
    p = coefficients["Pr(>|t|)"]
  )
  
  out_1 <- rbind(out_1, results)
  
  # Income
  model <- df %>%
    drop_na(pb_income_num) %>%
    pivot_longer(matches(paste0("y.*", y))) %>%
    lmerTest::lmer(data = .,
                   formula = value ~ pb_income_num + (1 | yb_lsmh_id)) %>%
    summary()
  
  coefficients <- model$coefficients[-1,]
  
  results <- tibble(
    DV = y,
    IV = "pb_income_num",
    est = coefficients["Estimate"],
    se = coefficients["Std. Error"],
    p = coefficients["Pr(>|t|)"]
  )
  
  out_1 <- rbind(out_1, results)
  
}

# p-adjust
out_1$p <- p.adjust(out_1$p, "BH")

# Report
out_1 %>%
  arrange(p) %>%
  kable() %>%
  kable_styling()
```

## Analysis 2: Belief Correlates

#### 2a. Relationship Between Child Beliefs

Repeated measures correlation (rmcorr)

```{r}
df_long_2a <- df %>%
  select(yb_lsmh_id, paste0("yb_", beliefs), paste0("y3m_", beliefs)) %>%
  pivot_longer(-yb_lsmh_id, 
               names_sep = "_",
               names_to = c("time", ".value"))

out_2a <- tibble()

for(x in beliefs) {
  
  for(y in beliefs) {
    
    if(x != y) {
      
      correlation <- rmcorr(
        data = df_long_2a,
        participant = "yb_lsmh_id",
        measure1 = x,
        measure2 = y
      )
      
      results <- tibble(
        x = x,
        y = y,
        r = correlation$r,
        p = correlation$p
      )
      
      out_2a <- rbind(out_2a, results)
      
    }
    
  }
  
}

# Remove redundancies
out_2a <- out_2a %>%
  rowwise() %>%
  mutate(xy = paste(sort(c(x, y)), collapse = " ")) %>%
  ungroup() %>%
  distinct(xy, .keep_all = T)


# p-adjust
out_2a$p <- p.adjust(out_2a$p, "BH")

# Report
out_2a %>%
  arrange(p) %>%
  kable() %>%
  kable_styling()
```

#### 2b: Relationship Between parent Beliefs

Repeated measures correlation (rmcorr)

```{r}
df_long_2b <- df %>%
  select(yb_lsmh_id, paste0("pb_", beliefs), paste0("p3m_", beliefs)) %>%
  pivot_longer(-yb_lsmh_id, 
               names_sep = "_",
               names_to = c("time", ".value"))

out_2b <- tibble()

for(x in beliefs) {
  
  for(y in beliefs) {
    
    if(x != y) {
      
      correlation <- rmcorr(
        data = df_long_2b,
        participant = "yb_lsmh_id",
        measure1 = x,
        measure2 = y
      )
      
      results <- tibble(
        x = x,
        y = y,
        r = correlation$r,
        p = correlation$p
      )
      
      out_2b <- rbind(out_2b, results)
      
    }
    
  }
  
}

# Remove redundancies
out_2b <- out_2b %>%
  rowwise() %>%
  mutate(xy = paste(sort(c(x, y)), collapse = " ")) %>%
  ungroup() %>%
  distinct(xy, .keep_all = T)


# p-adjust
out_2b$p <- p.adjust(out_2b$p, "BH")

# Report
out_2b %>%
  arrange(p) %>%
  kable() %>%
  kable_styling()
```

#### 2c: Child Belief Correlates

Repeated measures correlation (rmcorr)

```{r}
# Other constructs
psychVariables <- c("cdi", "bhs", "pcsc", "iptq", "shs")

df_long_2c <- df %>%
  select(yb_lsmh_id, 
         paste0("yb_", beliefs), paste0("y3m_", beliefs),
         paste0("yb_", psychVariables), paste0("y3m_", psychVariables)) %>%
  pivot_longer(-yb_lsmh_id, 
               names_sep = "_",
               names_to = c("time", ".value"))

out_2c <- tibble()

for(x in beliefs) {
  
  for(y in psychVariables) {
    
    correlation <- rmcorr(
      data = df_long_2c,
      participant = "yb_lsmh_id",
      measure1 = x,
      measure2 = y
    )
    
    results <- tibble(
      x = x,
      y = y,
      r = correlation$r,
      p = correlation$p
    )
    
    out_2c <- rbind(out_2c, results)
      
  }
  
}

# p-adjust
out_2c$p <- p.adjust(out_2c$p, "BH")

# Report
out_2c %>%
  arrange(p) %>%
  kable() %>%
  kable_styling()
```

## Analysis 3: Child Belief Stability

Spearman correlation (cor)

```{r}
out_3 <- tibble()

for(x in beliefs) {
  
  correlation <- cor.test(
    df[[paste0("yb_", x)]],
    df[[paste0("y3m_", x)]],
    use = "complete.obs"
  )
  
  results <- tibble(
    x = x,
    r = correlation$estimate,
    p = correlation$p.value
  )
  
  out_3 <- rbind(out_3, results)
  
}

# p-adjust
out_3$p <- p.adjust(out_3$p, "BH")

# Report
out_3 %>%
  arrange(p) %>%
  kable() %>%
  kable_styling()
```

## Analysis 4: Child and Parent Belief Agreement

Repeated measures correlation (rmcorr)

```{r}
df_long_4_y <- df %>%
  select(yb_lsmh_id, paste0("yb_", beliefs), paste0("y3m_", beliefs)) %>%
  pivot_longer(-yb_lsmh_id, 
               names_sep = "_",
               names_to = c("time", ".value")) %>%
  mutate(time = gsub("y", "", time))

df_long_4_p <- df %>%
  select(yb_lsmh_id, paste0("pb_", beliefs), paste0("p3m_", beliefs)) %>%
  pivot_longer(-yb_lsmh_id, 
               names_sep = "_",
               names_to = c("time", ".value")) %>%
  mutate(time = gsub("p", "", time))

df_long_4 <- inner_join(df_long_4_y, df_long_4_p, 
                        by = c("yb_lsmh_id", "time"),
                        suffix = c("_youth", "_parent"))

out_4 <- tibble()

for(x in beliefs) {
  
  correlation <- rmcorr(
    data = df_long_4,
    participant = "yb_lsmh_id",
    measure1 = paste0(x, "_youth"),
    measure2 = paste0(x, "_parent")
  )
  
  results <- tibble(
    x = x,
    y = y,
    r = correlation$r,
    p = correlation$p
  )
  
  out_4 <- rbind(out_4, results)
      
}

# p-adjust
out_4$p <- p.adjust(out_4$p, "BH")

# Report
out_4 %>%
  arrange(p) %>%
  kable() %>%
  kable_styling()
```
