---
title: "ADAA Presentation"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(easypackages)
libraries("tidyverse", "magrittr", "ggplot2", "scales", "corrplot", "knitr", "kableExtra", "conflicted")
walk(c("filter", "select", "count", "group_by"), ~ conflict_prefer(., "dplyr"))

knitr::opts_chunk$set(echo = F, message = F)

rm(list = ls())

df <- readRDS(file = "S:\\TRACK to TREAT\\Data\\Processed Data\\prognostic_pessimism_working_data.rds") %>%
  select(LSMHID,
         race, gender, age, famIncome,
         matches("cause_brain$"),
         matches("cause_env$"),
         matches("permanence$"),
         b.y.CDI2, b.y.malleability, b.y.hopelessness)

primary <- "#194656"
secondary <- "#B1E6DE"
```

### RQ 1: What are depressed adolescents’ beliefs about the causes (environmental versus genetic) and malleability (permanency) of depression?

Distributions

```{r}
df %>%
  pivot_longer(cols = c(b.y.cause_brain, b.y.cause_env, b.y.permanence)) %>%
  mutate(name = recode(name, 
                       "b.y.cause_brain" = "Cause: Brain",
                       "b.y.cause_env" = "Cause: Environment",
                       "b.y.permanence" = "Prognostic Pessimism")) %>%
  count(name, value) %>%
  drop_na() %>%
  ggplot() +
  geom_col(aes(value, n), fill = primary, width = .9) +
  facet_wrap(name ~ .) +
  scale_y_continuous(name = NULL) +
  scale_x_continuous(name = NULL, breaks = c(1, 5), labels = c("Not at all", "Completely")) +
  theme_classic() +
  theme(strip.background = element_rect(
    color = secondary, fill = secondary
  ))
```

Breakdown by Demographics

```{r}
df <- df %>%
  mutate(ageHigh = age > median(age),
         famIncomeHigh = famIncome >= median(famIncome))

aov(data = df, b.y.cause_brain ~ race) %>% summary()
aov(data = df, b.y.cause_env ~ race) %>% summary()
aov(data = df, b.y.permanence ~ race) %>% summary()

aov(data = df, b.y.cause_brain ~ gender) %>% summary()
aov(data = df, b.y.cause_env ~ gender) %>% summary()
aov(data = df, b.y.permanence ~ gender) %>% summary()

aov(data = df, b.y.cause_brain ~ ageHigh) %>% summary()
aov(data = df, b.y.cause_env ~ ageHigh) %>% summary()
aov(data = df, b.y.permanence ~ ageHigh) %>% summary()

aov(data = df, b.y.cause_brain ~ famIncomeHigh) %>% summary()
aov(data = df, b.y.cause_env ~ famIncomeHigh) %>% summary()
aov(data = df, b.y.permanence ~ famIncomeHigh) %>% summary()

df %>%
  rename(`Prognostic Pessimism` = b.y.permanence) %>%
  count(gender, `Prognostic Pessimism`) %>%
  mutate(gender = recode(gender, "NB" = "Non-Binary")) %>%
  ggplot() +
  geom_col(aes(`Prognostic Pessimism`, n), fill = primary, width = .9) +
  facet_wrap(gender ~ .) +
  scale_y_continuous(name = NULL) +
  scale_x_continuous(name = NULL, breaks = c(1, 5), labels = c("Not at all", "Completely")) +
  theme_classic() +
  theme(strip.background = element_rect(
    color = secondary, fill = secondary
  ))

df %>%
  group_by(gender) %>%
  summarize(mean = mean(b.y.permanence, na.rm = T))
```

### RQ 2: How do these beliefs relate to one another and to other relevant constructs (e.g., psychopathology severity)?

```{r}
df %>%
  select(`Cause: Brain` = b.y.cause_brain, 
         `Cause: Environment` = b.y.cause_env, 
         `Prognostic Pessimism` = b.y.permanence) %>%
  cor(use = "pairwise.complete.obs", method = "spearman") %>%
  corrplot(type = "lower", method = "number", tl.col = primary, tl.srt = 45)

df %>%
  select(`Prognostic Pessimism` = b.y.permanence, 
         `Depression Symptom Severity (CDI-2)` = b.y.CDI2, 
         `Fixed Mindset of Personality (IPTQ)` = b.y.malleability, 
         `Hopelessness (BHS-4)` = b.y.hopelessness) %>%
  cor(use = "pairwise.complete.obs", method = "spearman") %>%
  corrplot(type = "lower", method = "number", tl.col = primary, tl.srt = 45)
```

### RQ 3: Do children and parents hold similar beliefs?

```{r}
mean(df$b.y.cause_brain, na.rm = T)
mean(df$b.p.cause_brain, na.rm = T)
cor.test(df$b.y.cause_brain, df$b.p.cause_brain, method = "spearman")

mean(df$b.y.cause_env, na.rm = T)
mean(df$b.p.cause_env, na.rm = T)
cor.test(df$b.y.cause_env, df$b.p.cause_env, method = "spearman")

mean(df$b.y.permanence, na.rm = T)
mean(df$b.p.permanence, na.rm = T)
cor.test(df$b.y.permanence, df$b.p.permanence, method = "spearman")
```

### RQ 4: How stable are these beliefs?

```{r}
mean(df$b.y.cause_brain, na.rm = T)
mean(df$f.y.cause_brain, na.rm = T)
cor.test(df$b.y.cause_brain, df$f.y.cause_brain, method = "spearman")

mean(df$b.y.cause_env, na.rm = T)
mean(df$f.y.cause_env, na.rm = T)
cor.test(df$b.y.cause_env, df$f.y.cause_env, method = "spearman")

mean(df$b.y.permanence, na.rm = T)
mean(df$f.y.permanence, na.rm = T)
cor.test(df$b.y.permanence, df$f.y.permanence, method = "spearman")
```